Инструментарий анализа, классификации и интерпретации сцен

### 2022-09-01 paper-military-september-2022.tex
Added acknowledgements.

\renewcommand\refname{\centering Литература}
\begin{thebibliography}{99}
  % By alphabet
\bibitem{logtalk}Moura, P. (2011). Programming Patterns for Logtalk Parametric Objects. In: Abreu, S., Seipel, D. (eds) Applications of Declarative Programming and Knowledge Management. INAP 2009. Lecture Notes in Computer Science(), vol 6547. Springer, Berlin, Heidelberg. \url{https://doi.org/10.1007/978-3-642-20589-7_4}
\bibitem{dataflow}E. A. Lee, D. G. Messerschmitt, "Synchronous data flow," in Proceedings of the IEEE, vol. 75, no. 9, pp. 1235-1245, Sept. 1987, \doi{10.1109/PROC.1987.13876}.
\bibitem{zont19} E.~Cherkashin, A.~Shigarov, V.~Paramonov. Representation of MDA transformation with logical objects.  Procs. of International Multi-Conference on Engineering, Computer and Information Sciences (SIBIRCON), Novosibirsk, Russia, 2019, pp.~0913--0918 \doi{10.1109/SIBIRCON48586.2019.8958008}
\bibitem{kg} A.~Hogan, E.~Blomqvist, M.~Cochez, C.~D’Amato \emph{et al}. Knowledge Graphs, 2020. URL:\url{https://arxiv.org/abs/2003.02320v5} (access date: 12-Dec-2021)
\bibitem{azis}Y. Rhazali, Y. Hadi, A. Mouloudi. <<Model Transformation with ATL into MDA from CIM to PIM Structured through MVC,>> Procedia Computer Science 83 (2016) 1096–1101. URL:\url{https://doi.org/10.1016/j.procs.2016.04.229}
\bibitem{QVT} The MOF Query/View/Transformation Specification Version 1.1. URL:\url{http://www.omg.org/spec/QVT/1.1}
\bibitem{nikita} A.Y.~Yurin, N.O.~Dorodnykh, O.A.~Nikolaychuk, M.A.~Grishenko. Designing rule-based expert systems with the aid of the model-driven development approach. Expert Systems. 2018; 35:e12291. https://doi.org/10.1111/exsy.12291
\bibitem{b2} E.~Cherkashin, I.~Terehin, V.~Paramonov, V.~Tertychniy, <<New transformation approach for Model Driven Architecture,>> Proceedings of the 35th International Convention MIPRO, Opatija, 2012, p.~1082-1087.
\bibitem{GT} A. Belghiat, M. Bourahla. <<UML Class Diagrams to OWL Ontologies: A Graph Transformation based Approach,>> International Journal of Computer Applications. 41. pp.~41-46.

% \bibitem{uml2owl} UMLtoOWL: Converter from UML to OWL. URL: \url{http://www.sfu.ca/~dgasevic/projects/UMLtoOWL/}.
\bibitem{kuz}М.Б.~Кузнецов. Трансформация UML-моделей и ее использование в технологии MDA. // Программирование. 2007. Т. 33. № 1. С. 65-79.

>>>>

\textit{Исследование проведено в рамках проекта <<Методы и технологии облачной сервис-ориентированной цифровой платформы сбора, хранения и обработки больших объёмов разноформатных междисциплинарных данных и знаний, основанные на применении искусственного интеллекта, модельно-управляемого подхода и машинного обучения>>, №~госрегистрации 121030500071-2, номер в ИС:~FWEW-2021-0005.}
\renewcommand\refname{\centering Литература}
\begin{thebibliography}{99}
  % By alphabet
\bibitem{logtalk}Moura P. Programming Patterns for Logtalk Parametric Objects // In: Abreu, S., Seipel, D. (eds) Applications of Declarative Programming and Knowledge Management. INAP 2009. -- Lecture Notes in Computer Science -- Vol. 6547 -- Springer, Berlin, Heidelberg -- 2011. \doi{10.1007/978-3-642-20589-7_4}
\bibitem{dataflow}Lee E. A., Messerschmitt D. G. Synchronous data flow // In Proceedings of the IEEE -- vol. 75, no. 9 -- pp. 1235-1245, -- 1987, \doi{10.1109/PROC.1987.13876}.
\bibitem{zont19} Cherkashin E., Shigarov A., Paramonov V. Representation of MDA transformation with logical objects // Procs. of International Multi-Conference on Engineering, Computer and Information Sciences (SIBIRCON) Novosibirsk, Russia -- 2019 -- pp.~0913--0918 \doi{10.1109/SIBIRCON48586.2019.8958008}
\bibitem{kg} Hogan A., Blomqvist E., Cochez M., D’Amato C. \emph{et al}. Knowledge Graphs -- 2020 URL:\url{https://arxiv.org/abs/2003.02320v5} (access date: 12-Dec-2021)
\bibitem{azis}Rhazali Y., Hadi Y., Mouloudi A. Model Transformation with ATL into MDA from CIM to PIM Structured through MVC // Procedia Computer Science -- Vol. 83 -- 2016 -- pp. 1096–1101. \doi{10.1016/j.procs.2016.04.229}
\bibitem{QVT} The MOF Query/View/Transformation Specification Version 1.1. URL:\url{http://www.omg.org/spec/QVT/1.1}
\bibitem{nikita} Yurin A.Y., Dorodnykh N.O., Nikolaychuk O.A., Grishenko M.A. Designing rule-based expert systems with the aid of the model-driven development approach // Expert Systems -- 2018 -- 35:e12291. \doi{10.1111/exsy.12291}
\bibitem{b2} Cherkashin E., Terehin I., Paramonov V. New transformation approach for Model Driven Architecture // Proceedings of the 35th International Convention MIPRO, Opatija -- 2012 -- pp.~1082-1087.
\bibitem{GT} Belghiat A., Bourahla M.. UML Class Diagrams to OWL Ontologies: A Graph Transformation based Approach // International Journal of Computer Applications -- Vol. 41 -- pp.~41-46.

% \bibitem{uml2owl} UMLtoOWL: Converter from UML to OWL. URL: \url{http://www.sfu.ca/~dgasevic/projects/UMLtoOWL/}.
\bibitem{kuz}Кузнецов М.Б. Трансформация UML-моделей и ее использование в технологии MDA // Программирование -- Т. 33. № 1 -- 2007 -- С. 65--79.
